Unit tests

### 2018-03-09 Tests.Rmd
editorial

>>>>

We decided not to use the goodness-of-fit tests for normal copulas (`gofnormal=F` henceforth)
because it takes so long, and the model-selection results give 
sufficient indication that the normal copula is not well supported. 
Finally, in other simulations we have discovered the goodness-of-fit
tests for the normal copula have limited statistical power.
